`traveltime`: an R package to calculate walking and motorised travel time from user-specified locations

### 2025-02-06 paper/paper.qmd
Roll back figure cross refs from #47 in attempt to address #43 - use \ref{figure} format instead of @figure which quarto likes - this breaks the html render by I think it should make the draft-yml action render the cross refs.
If this fails might need to roll back chunks

Below we plot the friction surface raster `friction_singapore`, with the vector boundary `singapore_shapefile` as a grey line, and `stations` as grey points (Figure @fig-data). Higher values of friction indicate more time travelling across a given cell.

@@

We present the resulting calculated travel times in Figure @fig-result. Note that the results in `travel_timesingapore` include infinite (`Inf`) values. In Figure @fig-data, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in Figure @fig-result. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in Figure @fig-result.

>>>>

Below we plot the friction surface raster `friction_singapore`, with the vector boundary `singapore_shapefile` as a grey line, and `stations` as grey points (Figure \ref{fig-data}). Higher values of friction indicate more time travelling across a given cell.

@@

We present the resulting calculated travel times in Figure \ref{fig-result}. Note that the results in `travel_timesingapore` include infinite (`Inf`) values. In Figure \ref{fig-data}, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in Figure \ref{fig-result}. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in Figure \ref{fig-result}.
